\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-07 k-planar.tex
Pfffffft

We first formally define $k$-planar graphs.  An \defin{embedded graph} $G$ is a graph with $V(G)\subset\R^2$ in which each edge $vw\in E(G)$ is a curve\footnote{A \defin{curve} in a surface $\Sigma$ is a continuous function $f:[0,1]\to \Sigma$. The points $f(0)$ and $f(1)$ are called the \defin{endpoints} of the curve.  When there is no danger of misunderstanding we treat a curve $f$ as the point set $\{f(t):0\le t\le 1\}$.} in $\R^2$ with endpoints $v$ and $w$ and not containing any vertex of $G$ in its interior.  A \defin{crossing} in an embedded graph $G$ is a triple $(p,vw,xy)$ with $p\in\R^2$, $vw,xy\in E(G)$ and such that $p\in (vw\cap xy)\setminus\{v,w,x,y\}$. An embedded graph $G$ is \defin{$k$-plane} if each edge of $G$ takes part in at most $k$ crossings. \note{DW}{We need to assume that at most two edges cross at a single point, so we can add a dummy vertex of degree 4, right?}\note{PM}{No, under the current definition, $r$ edges crossing at a single point $p$ generate $\binom{r}{2}$ crossings, with each edge taking part in $r-1$ crossings, just like they would if we perturbed the edges so that they all crossed at individual points.  I guess we could mention this.  (See the first paragraph in the proof of Theorem~2 below.)}  A (not necessarily embedded) graph $G'$ is \defin{$k$-planar} if there exists a $k$-plane graph $G$ isomorphic to $G'$. Under these definitions, $0$-planar graphs are exactly planar graphs and $0$-plane graphs are exactly plane graphs.

@@

>>>>

We first formally define $k$-planar graphs.  An \defin{embedded graph} $G$ is a graph with $V(G)\subset\R^2$ in which each edge $vw\in E(G)$ is a curve\footnote{A \defin{curve} in a surface $\Sigma$ is a continuous function $f:[0,1]\to \Sigma$. The points $f(0)$ and $f(1)$ are called the \defin{endpoints} of the curve.  When there is no danger of misunderstanding we treat a curve $f$ as the point set $\{f(t):0\le t\le 1\}$.} in $\R^2$ with endpoints $v$ and $w$ and not containing any vertex of $G$ in its interior.  A \defin{crossing} in an embedded graph $G$ is a triple $(p,vw,xy)$ with $p\in\R^2$, $vw,xy\in E(G)$ and such that $p\in (vw\cap xy)\setminus\{v,w,x,y\}$. An embedded graph $G$ is \defin{$k$-plane} if each edge of $G$ takes part in at most $k$ crossings. \note{DW}{We need to assume that at most two edges cross at a single point, so we can add a dummy vertex of degree 4, right?}\note{PM}{No, under the current definition, $r$ edges crossing at a single point $p$ generate $\binom{r}{2}$ crossings, with each edge taking part in $r-1$ crossings, just like they would if we perturbed the edges so that each pair crosses at a distinct point.  I guess we could mention this.  (See the first paragraph in the proof of Theorem~2 below.)}  A (not necessarily embedded) graph $G'$ is \defin{$k$-planar} if there exists a $k$-plane graph $G$ isomorphic to $G'$. Under these definitions, $0$-planar graphs are exactly planar graphs and $0$-plane graphs are exactly plane graphs.

@@

\note{PM}{I agree that we should fix it and keep it.  Another reason: For vertex ranking, the bound is $O(\log n/\log^{(t)} n)$ where $t:=\tw(H)$, so this is an example where $\tw(H)$ affects more than just the constant.}
